Supplement 4: Spatial Correlations

### 2024-01-10 Code/Supplement 4_Spatial Correlations.Rmd
add caption to figure
per journal review request re copyright

WIS_map %>%
  ggplot(., aes(fill = log(scaled_rel_skill))) +
  geom_sf(color = "grey65") + 
  facet_wrap(~order_fact) +
  theme_void() +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 0, na.value = "grey75", 
                       name = "State-Level Relative\nWeighted Interval Score", 
                       breaks = c(-1,0,1,2), 
                       labels =c("0.5", 1, 2, 3)) + 
  labs(caption="*National rWIS < 1.0") +
  theme(plot.margin = unit(c(0,0,0,0), "cm"),
        strip.background=element_blank(), strip.text=element_text(size = 10, face='bold'),
        legend.justification = c(1,0), legend.position=c(0.90, 0.10),
        legend.direction = "horizontal")

>>>>

WIS_map %>%
  ggplot(., aes(fill = log(scaled_rel_skill))) +
  geom_sf(color = "grey65") + 
  facet_wrap(~order_fact) +
  theme_void() +
  scale_fill_gradient2(low = "steelblue", high = "red", midpoint = 0, na.value = "grey75", 
                       name = "State-Level Relative\nWeighted Interval Score", 
                       breaks = c(-1,0,1,2), 
                       labels =c("0.5", 1, 2, 3)) + 
  labs(caption="*National rWIS < 1.0\nThe base layer for this map was created with ggplot2 (https://ggplot2.tidyverse.org/reference/map_data.html).") +
  theme(plot.margin = unit(c(0,0,0,0), "cm"),
        strip.background=element_blank(), strip.text=element_text(size = 10, face='bold'),
        legend.justification = c(1,0), legend.position=c(0.90, 0.10),
        legend.direction = "horizontal")
